Stock enhancement undermines community stability

### 2022-02-03 rmd/supporting_info.Rmd
Update supporting_info.Rmd

Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**). We identified five influential parameters (**Table S2-4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`). Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`). This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.

@@

We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data. Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate. We summarized the estimated parameters and reconstructed community dynamics in **Table S7** and **Figures S13-S15** .

@@

```{=tex}
\begin{align}
\left\{
\begin{aligned}
\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
\end{aligned}
\right.
\end{align}
```
$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$. The site-level predictors include upstream watershed area, air temperature, precipitation, and proportion of forest land use. The watershed-specific intercept was related to watershed-level predictors as:

@@

We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016]. We assigned weakly informative priors to parameters (**Table S6**). Three Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged. Total MCMC interations ranged from `r min(df_mcmc_ssm$n_total_mcmc)` to `r max(df_mcmc_ssm$n_total_mcmc)` for the state-space models and was `r unique(df_mcmc_reg$n_total_mcmc)` for the regression models. The first `r unique(c(df_mcmc_ssm$n_burn, df_mcmc_reg$n_burn))` iterations were discarded as burn-in, and MCMC samples were saved every `r unique(df_mcmc_ssm$n_thin)` (state-space) and `r unique(df_mcmc_reg$n_thin)` iterations (regression) to reduce autocorrelation. Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached \< 1.1 [@gelmanDataAnalysisUsing2007]. Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].

@@

For each parameter combination, we regressed the mean densities and SDs of the whole community, enhanced species, and unenhanced species $y_j$ on the number of releases $R$ as:

$$
\begin{aligned}
  y_j &\sim Normal(\mu_j, \sigma^2)\\
  \mu_j &= \xi_0 + \xi_1~R_j
\end{aligned}
$$

where $\xi_k$ ($k = 0-1$) are the intercept ($\xi_0$) and regression coefficient ($\xi_1$). We extracted 500 estimates of $\xi_1$, each of which represents the effect of stock enhancement $R$ on community dynamics under a given parameter combination. To examine influences of simulation parameters (**Table S1**) on $\xi_1$, we developed the following regression model taking $\xi_1$ as a response variable (parameter combination $n$):

$$
\begin{aligned}
  \xi_{1,n} &\sim Normal(\mu_n, \sigma^2)\\
  \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 r_{1,n} + \zeta_3 r_{max,n} + \zeta_4  \bar{\alpha}_n + \zeta_5 K_n + \zeta_6 \sigma_{\epsilon,n} + \zeta_7 f_{R, n}
\end{aligned}
$$

where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$). Both response and explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.

We found that regression coefficients of the following parameters ($\zeta$) never exceeded a value of 0.30 and were less influential: the number of species $S$, the maximum intrinsic growth rate of unenhanced species $r_{max}$, and relative fitness $f_R$. Therefore, in the main simulation, we fixed values of $S$ and $r_{max}$ (**Table S1**). In the meantime, we varied values of $K$, $r_1$, $\sigma_{\epsilon}$, $f_R$, and $\bar{\alpha}$ as they are potentially influential (**Table S1**). Although $f_R$ had little influence on stocking effects (**Table S1**), we varied this parameter given the significant interest in the relative fitness of captive-bred individuals in the wild.

@@

# Figure S1-12
## load figures
source(here::here("code/figure_si_theory.R"))

@@

  knit_chunk <- paste0("## Figure S", i + j,
                       " Theoretical prediction (",
                       "$r_1$ = `r df_param$r1[",i,"]`, ",
                       "$\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`, ",
                       "$K$ = `r df_param$k[",i,"]`) \n",

@@

                       "Theoretical predictions for the stocking effect on community dynamics. Rows represent different response variables, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$). Other parameters are: ",
                       "intrinsic growth rate of enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
                        "environmental variability $\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`; ",
                        "carrying capacity $K$ = `r df_param$k[",i,"]`.",
                        "\n\\pagebreak\n")

@@

# Figure S13-15
## load figures
source(here::here("code/figure_si_obs_dyns.R"))
j <- 12

@@

>>>>

Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**). We identified five influential parameters (**Table S2-S4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`). Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`). This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.

@@

We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data. Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate. We summarized the reconstructed community dynamics in **Figures S7-S9**.

@@

```{=tex}
\begin{align}
\left\{
\begin{aligned}
\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
\end{aligned}
\right.
\end{align}
```
$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$. The site-level predictors include upstream watershed area, air temperature, precipitation, and forest land use. Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**). The watershed-specific intercept was related to watershed-level predictors as:

@@

We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016]. We assigned weakly informative priors to parameters (**Table S6**). Three Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged. Total MCMC interations ranged from `r min(df_mcmc_ssm$n_total_mcmc)` to `r max(df_mcmc_ssm$n_total_mcmc)` for the state-space models and was `r unique(df_mcmc_reg$n_total_mcmc)` for the regression models. The first `r unique(c(df_mcmc_ssm$n_burn, df_mcmc_reg$n_burn))` iterations were discarded as burn-in, and MCMC samples were saved every `r unique(df_mcmc_ssm$n_thin)` (state-space) and `r unique(df_mcmc_reg$n_thin)` iterations (regression) to reduce autocorrelation. Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached \< 1.1 [@gelmanDataAnalysisUsing2007]. Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021]. Parameter estimates were summarized in **Table S7-S10**.

@@

For each parameter combination, we estimated Spearman's rank correlation $\xi$ between the number of releases $R$ and community statistics (the mean densities and SDs of the whole community, enhanced species, and unhenaced species). To examine influences of simulation parameters on $\xi$ (**Table S1**), we developed the following regression model taking $\xi$ as a response variable (parameter combination $n$):

$$
\begin{aligned}
  \xi_{n} &\sim Normal(\mu_n, \sigma^2)\\
  \mu_n &= \zeta_0 + \zeta_1 S_n + \zeta_2 r_{1,n} + \zeta_3 r_{max,n} + \zeta_4  \bar{\alpha}_n + \zeta_5 K_n + \zeta_6 \sigma_{\epsilon,n} + \zeta_7 f_{R, n}
\end{aligned}
$$

where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$). Explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.

We found that regression coefficients of the following parameters ($\zeta$) never exceeded a value of 0.10: the number of species $S$, maximum intrinsic growth rate of unenhanced species $r_{max}$, environmental stochasticity $\sigma_{\epsilon}$, and relative fitness $f_R$. Therefore, these parameters have little influence on the qualitative relationship between the number of releases and community dynamics. In the main simulation, we fixed values of $S$, $r_{max}$, and $\sigma_{\epsilon}$ (**Table S1**). In the meantime, we varied values of $K$, $r_1$, $f_R$, and $\bar{\alpha}$ as they are potentially influential (**Table S1**). Although $f_R$ had little influence on stocking effects (**Table S1**), we varied this parameter given the significant interest in the relative fitness of captive-bred individuals in the wild.

@@

# Figure S1-6
## load figures
source(here::here("code/figure_si_theory.R"))

@@

  knit_chunk <- paste0("## Figure S", i + j,
                       " Theoretical prediction (",
                       "$r_1$ = `r df_param$r1[",i,"]`, ",
                       "$K$ = `r df_param$k[",i,"]`) \n",

@@

                       "Theoretical predictions for the stocking effect on community dynamics. Rows represent different response variables, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$). Other parameters are: ",
                       "number of species $S$ = `r df_param$n_species[",i,"]`; ",
                       "intrinsic growth rate of an enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
                       "maximum intrinsic growth rate of unenhanced species $r_{max}$ = `r df_param$r_max[",i,"]`; ",
                        "environmental stochasticity $\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`; ",
                        "carrying capacity $K$ = `r df_param$k[",i,"]`.",
                        "\n\\pagebreak\n")

@@

# Figure S7-9
## load figures
source(here::here("code/figure_si_obs_dyns.R"))
j <- 6

@@

## Figure S10 Environmental variables

```{r figure_s10, fig.width=11, fig.height=8}

source(here::here("code/figure_si_env.R"))

print(g_env)
```

Distribution of environmental variables in the protected watershed. Note that the number of fish released and ocean productivity (chlorophyll a) are measured at the watershed level while others are measured at the site level.

## Figure S11 Correlation plot

```{r figure_s11, fig.width=11, fig.height=11}

source(here::here("code/figure_si_cor.R"))
```

Correlation plot among environmental variables in the protected watersheds. Numbers indicate Spearman's rank correlations.
